Multisensor Architecture for an Intersection Management System

### 2018-02-18 ch3-arch_sys.tex
Updated chapter 1 and 3

Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors manufacturing and computing capabilities. Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control step. It is also needed to test and validate the developments prior to a real and full functional implementation. The first part of this chapter describes the main stages in a intersection management system based on image and range sensors, and the methods used in these stages. Then an architecture proposal for the implementation of such a system is presented. Finally, two validation tools for IMS applications are described, simulation models and datasets.

@@

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene. Spatial-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, including common task performed at each of these stage and also is shown how the data volume is reduced while data meaning increases in the last stages.

@@

\section{Methods and techniques}

Different tasks could be performed in each one of aforementioned stages, as is referred in figure \ref{proc_stages_tasks}. Below there is a description of common concepts and methods associated with each of these tasks, some of them are sensor-independent and others are focused on a specific sensor or type of data. Additionally, these tasks could be used as fusion blocks for homogeneous or heterogeneous data.

@@

The proposal presented in this work is based on MFI model processing entities in the sense that a processing block could take one or more inputs related between them and generate an output of the same type or a higher level output. The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from.

@@

>>>>

Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors manufacturing and computing capabilities. Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control stages. It is also needed to test and validate the developments prior to a real and full functional implementation. The first part of this chapter describes the main stages in a intersection management system, from data preprocessing to situation assesment. Then, two validation tools for IMS applications are described, simulation models and datasets. And finally, the proposed architecture for the implementation of an IMS system is presented.

@@

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene. Spatial-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situations or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, including common task performed at each of these stage and also is shown how the data volume is reduced while data meaning increases in the last stages.

@@

@@

The proposal presented in this work is based on MFI model processing entities in the sense that a processing block could take one or more inputs related between them and generate an output of the same type or a higher level output. The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from. Three main components of the architecture are defined: Data model, communication scheme and  processing blocks.

@@

The data model proposed for the system includes the abstraction of the sensing elements and the intersection itself. For the sensing elements is created a Sensor base class and two derived classes for different type of sensors, Laser class and Camera class.
